Reproduction

### 2024-11-04 pages/reproduction.qmd
docs(reproduction): add reflections on reproduction success and timings

<!--TODO: Consider changing this figure to have lines straight directly connecting points rather than steps, as that would prevent overlap between hernandez and wood? However, time to event data is usually plot like that. -->

@@

**TODO: Where possible, reflect on what I think to be the primary reason that didn't manage to fully reproduce despite troubleshooting, for the studies where this was the case**

@@

**TODO: Reflect on these timings - what I think were the primary reason for things to be quicker or slower - and what I think was relevant/important** <!--e.g. models with run long times, experimenting with parameters to run it quicker, in order to more easily troubleshoot, else run for long time then discover xyz is wrong-->

>>>>

<!--Note: In this figure, Hernandez and Wood overlap. Although we would typically have stepped lines like this for time-to-event data, I did explore switching to diagonals to avoid the overlap, but then realised we just get the same issue except with Johnson and Hernandez almost exactly overlapping. -->

@@

For the studies where I didn't manage to fully reproduce results despite troubleshooting, my reflections on what I think to be the primary reason for not managing to reproduce results in each case were:

**@shoaib_simulation_2021:** No specific suggestions - had to write code to run scenarios and process results, so it could be that I hadn't done this all exactly the same as in the original study.

**@huang_optimizing_2019:** No specific suggestions - had to write code to run scenarios and process results, so it could be that I hadn't done this all exactly the same as in the original study.

**@johnson_cost_2021:** No specific suggestions - although note that their results on GitHub appeared to likewise have the same discrepancy compared with the article, so it appears there might have been a minor change to the code/parameters made from that used to produce the article figure that might explain this.

**@hernandez_optimal_2015:** This appears likely to be due to a parameter somewhere being not quite right. Ivan Hernandez suggested that it could be a random seed or that the optimisation doesn't have enough runs - although was using the same seed and played around with run number. The other suggestion was that the version on GitHub might not have exactly the right version of inputs - and interestingly, he had an earlier version of the paper that had more similar results (our discrepancy was in range on Y axis, and he had an earlier version with range of 0 to 15000). This reaffirms that a minor parameter difference is the likely reason for the discrepancy, with that having impacted across nearly all the results.

@@

There was a large amount of variation in the time each reproduction took. For each study, I have also reflected on what I think were the primary reasons behind things being quicker or slower:

**@shoaib_simulation_2021** - 28h 14m:

* This had lots of items to reproduce (17)
* Took me longer than usual to set up environment as needed specific package versions and had some confusion around package `statistics` which is base but I had mixed up with one that can be imported from conda/pypi
* Most of the time was dedicated to identifying parameters for each scenario, writing code to run the scenarios (and run these programmatically), and writing code to process the results into figures and tables.

**@huang_optimizing_2019** - 24h 10m:

* Time-consuming aspects were modifying the code from the app so I could run it, writing code for each scenario, and writing code for figures (it took me quite a whiole to work out transformations for axes and how to standardise density)

**@lim_staff_2020** - 12h 27m:

* Lots of time was spent setting up model so could run programmatically, writing code for scenarios, and writing code to produce figures.

**@kim_modelling_2021** - 14h 42m:

* Time-consuming aspect was largely writing code to produce tables and figures (including figuring out how to process).

**@anagnostou_facs-charm_2022** - 2h 11m:

* This only had one item to reproduce.
* It required very little troubleshooting - just had to write code to produce figure, although it was relatively simple.

**@johnson_cost_2021** - 19h 49m:

* Most time was spent on writing code for sensitivity analysis, and to produce tables and figures (which included working out which results tables / columns / scenarios to use, how to transform columns, and how to calculate features like efficiency frontier)

**@hernandez_optimal_2015** - 17h 56m:

* Time-consuming aspects were writing code for scenarios and for figures and tables, and troubleshooting parameter discrepancies.

**@wood_value_2021** - 3h 50m:

* Ran quick as code for model didn't require troubleshooting (included all correct parameters and scenarios), and as they provided code to produce the figures and tables.

Regarding run time of the models themselves, for longer models, I sometimes experimented with parameters to run it quicker, in order to more easily troubleshoot, else I would run for a long time and then discover XYZ is wrong. Although the model run time itself is not included in the times, it is important to note, as some models took several days, and so in practice, this would impact on someone if they were trying to run a model within a short amount of time.

Regarding the reproduction run times, I think the main reflection from above is that including code with correct parameters and scenarios, and code to make the figures and tables, has a really big impact.
